---
title: "janette_file"
author: "Janette Avelar"
date: '2023-03-02'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(rio)
#all survey data
survey_2019 <- import(here("data", "schools_2018-19.csv"))
survey_2021a <- import(here("data", "schools_2020-21a.csv"))
survey_2021b <- import(here("data", "schools_2020-21b.csv"))
survey_2021c <- import(here("data", "schools_2020-21c.csv"))
survey_2022 <- import(here("data", "schools_2021-22.csv"))
```

Variables of interest:
* FRPL percent  
* BIPOC percent  
* Geographic locale  
* Year  
* Wave  
* 9 Tags (see below)

*We identified within that document the following tags- We are highlighting in light green the tags that are within that Ed justice and holistic student support cluster 1. There are 9 found within the cluster that are found across years. *
* Culturally responsive practices  
* Assessment for social-emotional learning  
* Family and community support services  
* Mental health services  
* Restorative practices  
* Designed to meet the students who have been marginalized  
* SEL curriculum  
* SEL integration school wide  
* Reallocation of school services 


# Clean 2018-19 Data
*Note* I named all datasets by the ending year. AY 2018-19 is now considered 2019, AY 2020-21 is now considered 2021, and AY 2021-22 is now considered 2022.

```{r subset 2019}
#Subset to relevant variables + NCES ID (key for merging)
merge_2019 <- survey_2019 %>% 
  select(nces_id, school_id, school_name, school_state, culturally_relevant, measures_sel, community_support, mental_health, restorative_practice, design_margins, sel_curriculum, sel_integrated, reallocation_resources, asian_percent, hispanic_percent, black_percent, white_percent, multiple_races_percent, hawaiian_native_percent, native_percent, locale, FRPL_percent) %>% 
  rename_at(vars(5:13), function(x){paste0("practices_", x)}) %>% 
  janitor::clean_names() %>% 
  # create BIPOC percent variable
  mutate_at(vars(ends_with("_percent")), str_remove_all, "%") %>% 
  mutate_at(vars(ends_with("_percent")), as.numeric) %>% 
  mutate(bipoc_percent = 100 - white_percent) %>% 
  select(!c(asian_percent, hispanic_percent, black_percent, white_percent, multiple_races_percent, hawaiian_native_percent, native_percent)) %>% 
  # add year and wave columns
  mutate(year = rep(2019, 173),
         wave = rep(1, 173)) %>% 
  # fill in not tagged **************NOT WORKING************
  mutate_at(vars(starts_with("practices_")), replace_na, 0)
#will need to double check that practices names match over time
#also need to pull in 0s for not tagged (I think it's currently NAs)
```

# Merge & Clean 2020-21 Data

*Notes:*
* Some practice names changed between 2019 and 2021 **need to mod before merging**  
* Wave coded as `2` for all in 2021 for ease, but can distinguish between waves 2 & 3 if needed

```{r}
# Prep each subset individually, then merge for one single dataset
# 2021 part 1
merge_2021a <- survey_2021a %>% 
  select(NCES_id, school_id, school_name, school_state, culturally_relevant, assessments_sel, community_supports, mental_health, restorative_practice, design_equity, sel_curriculum, sel_integrated, reallocation_resources, white_percent, locale, FRPL_percent) %>% 
  janitor::clean_names() %>% 
  #rename variables first
  rename_at(vars(5:13), function(x){paste0("practices_", x)}) %>% 
  #empty practices = 0 and time implemented = 1
  mutate_at(vars(starts_with("practices_")), function(x){case_when(x == "" ~ 0,
                                                                   x == 1 ~ 1,
                                                                   x != 0 & x != 1 ~ 1)}) %>% 
  #create BIPOC percent ***********can pull into custom function*************
  mutate_at(vars(ends_with("_percent")), str_remove_all, "%") %>% 
  mutate_at(vars(ends_with("_percent")), as.numeric) %>% 
  mutate(bipoc_percent = 100 - white_percent) %>% 
  select(!white_percent) %>% 
  #create wave and year columns
  mutate(year = rep(2021, 144),
         wave = rep(2, 144))

# 2021 part 2
merge_2021b <- survey_2021b %>% 
  select(NCES_id, school_id, school_name, school_state, culturally_relevant, assessments_sel, community_supports, mental_health, restorative_practice, design_equity, sel_curriculum, sel_integrated, reallocation_resources, white_percent, locale, FRPL_percent) %>% 
  janitor::clean_names() %>% 
  #rename variables first
  rename_at(vars(5:13), function(x){paste0("practices_", x)}) %>% 
  #empty practices = 0 and time implemented = 1
  mutate_at(vars(starts_with("practices_")), function(x){case_when(x == "" ~ 0,
                                                                   x == 1 ~ 1,
                                                                   x != 0 & x != 1 ~ 1)}) %>% 
  #create BIPOC percent ***********can pull into custom function*************
  mutate_at(vars(ends_with("_percent")), str_remove_all, "%") %>% 
  mutate_at(vars(ends_with("_percent")), as.numeric) %>% 
  mutate(bipoc_percent = 100 - white_percent) %>% 
  select(!white_percent) %>% 
    #create wave and year columns
  mutate(year = rep(2021, 88),
         wave = rep(2, 88))

#2021 part 3
# I believe this one does not need to be added - it was 2 waves, with the final survey checking up on COVID-specific practices
# will need to verify

# merge A & B
merge_2021 <- merge_2021a %>% 
  full_join(merge_2021b, by = c("nces_id", "school_id", "school_name", "school_state", "practices_culturally_relevant", "practices_assessments_sel", "practices_community_supports", "practices_mental_health", "practices_restorative_practice", "practices_design_equity", "practices_sel_curriculum", "practices_sel_integrated", "practices_reallocation_resources", "locale", "frpl_percent", "bipoc_percent", "year", "wave"))
```

# Subset 2022 Data

```{r subset 2022}
merge_2022 <- survey_2022 %>% 
  select(nces_id, school_id, school_name, school_state, practices_culturally_responsive, practices_assessments_sel, practices_community_supports, practices_mental_health, practices_restorative, practices_design_marginalized, practices_sel_curriculum, practices_sel_integrated, practices_reallocation_resources, white_percent, locale, frpl_percent) %>% 
  #create bipoc percent
  mutate(bipoc_percent = 100*(1 - white_percent)) %>% 
  select(!white_percent) %>% 
  #standardize frpl
  mutate(frpl_percent = frpl_percent*100,
   #create year and wave cols        
         year = rep(2022, 161),
         wave = rep(3, 161))
```

# Prep for merging

Current practice names:  
* Culturally responsive practices  
** 2019: `practices_culturally_relevant`  
** 2021: `practices_culturally_relevant`  
** 2022: `practices_culturally_responsive`  
*New var name*: `prac_culture`  

* Assessment for social-emotional learning  
** 2019: `practices_measures_sel`  
** 2021: `practices_assessments_sel`  
** 2022: `practices_assessments_sel`  
*New var name*: `prac_sel_assess`

* Family and community support services  
** 2019: `practices_community_support`  
** 2021: `practices_community_supports`  
** 2022: `practices_community_supports`  
*New var name*: `prac_community`

* Mental health services  
** 2019: `practices_mental_health`  
** 2021: `practices_mental_health`  
** 2022: `practices_mental_health`  
*New var name*: `prac_mental`

* Restorative practices 
** 2019: `practices_restorative_practice`  
** 2021: `practices_restorative_practice`  
** 2022: `practices_restorative`  
*New var name*: `prac_restorative`  

* Designed to meet the students who have been marginalized  
** 2019: `practices_design_margins`  
** 2021: `practices_design_equity`  
** 2022: `practices_design_marginalized`  
*New var name* `prac_marginalized`  

* SEL curriculum  
** 2019: `practices_sel_curriculum`  
** 2021: `practices_sel_curriculum`  
** 2022: `practices_sel_curriculum`  
*New var name*: `prac_sel_curriculum`  

* SEL integration school wide  
** 2019: `practices_sel_integrated`  
** 2021: `practices_sel_integrated`  
** 2022: `practices_sel_integrated`  
*New var name*: `prac_sel_integrated`

* Reallocation of school services
** 2019: `practices_reallocation_resources`  
** 2021: `practices_reallocation_resources`  
** 2022: `practices_reallocation_resources`  
*New var name*: `prac_resources`  

```{r merge prep}
#rename 2019
merge_2019 <- merge_2019 %>% 
  rename(
   "prac_culture" = practices_culturally_relevant,
   "prac_sel_assess" = practices_measures_sel,
   "prac_community" =  practices_community_support,
   "prac_mental" = practices_mental_health,
   "prac_restorative" = practices_restorative_practice,
   "prac_marginalized" = practices_design_margins,
   "prac_sel_curriculum" = practices_sel_curriculum,
   "prac_sel_integrated" = practices_sel_integrated,
   "prac_resources" = practices_reallocation_resources
  )
# rename 2021
merge_2021 <- merge_2021 %>% 
  rename(
   "prac_culture" = practices_culturally_relevant,
   "prac_sel_assess" = practices_assessments_sel,
   "prac_community" =  practices_community_supports,
   "prac_mental" = practices_mental_health,
   "prac_restorative" = practices_restorative_practice,
   "prac_marginalized" = practices_design_equity,
   "prac_sel_curriculum" = practices_sel_curriculum,
   "prac_sel_integrated" = practices_sel_integrated,
   "prac_resources" = practices_reallocation_resources
  )
# rename 2022
merge_2022 <- merge_2022 %>% 
  rename(
   "prac_culture" = practices_culturally_responsive,
   "prac_sel_assess" = practices_assessments_sel,
   "prac_community" =  practices_community_supports,
   "prac_mental" = practices_mental_health,
   "prac_restorative" = practices_restorative,
   "prac_marginalized" = practices_design_marginalized,
   "prac_sel_curriculum" = practices_sel_curriculum,
   "prac_sel_integrated" = practices_sel_integrated,
   "prac_resources" = practices_reallocation_resources
  )
```

# MERGE!

```{r merge}
# merge 2019, 2021, & 2022
main <- merge_2019 %>% 
  full_join(merge_2021, by = c("nces_id", "school_id", "year", "wave", "school_name", "school_state", "locale", "frpl_percent", "bipoc_percent", "prac_culture", "prac_sel_assess", "prac_community", "prac_mental", "prac_restorative", "prac_marginalized", "prac_sel_curriculum", "prac_sel_integrated", "prac_resources")) %>% 
  full_join(merge_2022, by = c("nces_id", "school_id", "year", "wave", "school_name", "school_state", "locale", "frpl_percent", "bipoc_percent", "prac_culture", "prac_sel_assess", "prac_community", "prac_mental", "prac_restorative", "prac_marginalized", "prac_sel_curriculum", "prac_sel_integrated", "prac_resources"))
# rename merge datasets
schools_2019 <- merge_2019
schools_2021 <- merge_2021
schools_2022 <- merge_2022
#save new dataset
# save(main, schools_2019, schools_2021, schools_2022,
#      file = "canopy-schools.RData")
```

