---
title: "tony_file"
author: "Tony Daza"
date: "2023-03-16"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true 
    code_folding: hide
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(needs)
library(lme4)  
library(Rmisc)
library(sjPlot)
needs(tidyverse, rio, here, psych)
```

# Innovative School Practices   
## Importing the Data  

Thank you Janette for compiling the data!

```{r import}

load(here("data/canopy-schools.RData"))


```

*After looking at the data, I think we need to combine the tags into one variable as a count of number of practices if we are going to run the model as suggested*

## Counting Number of Practices  

```{r count}
main$prac_tot <- rowSums(main[c(5,6,7,8,9,10,11,12,13)], na.rm=TRUE)

main <- main %>% mutate_at(c('locale'), ~na_if(.,''))

main$locale <- as.factor(main$locale)


count(main)

main %>%
  count(locale)

# Looks like we have 92 NA value schools.

```

## Examining data to model   

```{r desript}

main %>%
  filter(locale != "NA") %>%
  group_by(locale) %>%
ggplot(aes(x = wave, y = prac_tot )) +           
  geom_bar(stat = "summary", fun = "mean", fill="cornflowerblue") + 
  facet_grid(~locale) + 
  theme_classic()+
  labs(y = "Total Practices", x = "Wave")


```

**Add descriptive data**


## Fixed Effects  

This is how he did assignment 3 where we first examined if practices changed overtime in general without any predictors. 

```{r}
main$cwave <- c(scale(main$wave, center = TRUE, scale =TRUE))
main$cbipoc_percent <- c(scale(main$bipoc_percent,  center=TRUE, scale=TRUE)) 
main$cfrpl_percent <- c(scale(main$frpl_percent,  center=TRUE, scale=TRUE))

GLMMfix0 <- glmer(prac_tot ~ 1 + wave + (1|school_id), 
                  family = poisson, 
                  data = main) 
summary(GLMMfix0)

```
In this case, wave does seem to be significant. 

## Model with predictors  

Here we are adding in locale, percent bipoc, and percent frpl as predictors in our model. 

```{r}
library(lme4) 


GLMMfix <- glmer(prac_tot ~ 1 + wave + locale + bipoc_percent + frpl_percent + (1|school_id), 
                  family = poisson, 
                  data = main) 
## Not happy. Model failed to converge
## Will try to rescale variables

```

## Model Rescaled predictors   

The previous model failed to converge. I rescaled the predictors and now it converges. In this model we also have the interaction between wave and locale but not of percent bipoc and percent frpl.  


**The model did not converge without centering the data. Why is that?**

```{r}


GLMMfix1 <- glmer(prac_tot ~ 1 + cwave + 
                    locale + 
                    cbipoc_percent + 
                    cfrpl_percent + 
                    locale*cwave +
                    (1|school_id), 
                  family = poisson, 
                  data = main) 
summary(GLMMfix1)
tab_model(GLMMfix1)


```

**Add ICC**

In this model it seems like the interaction between wave and urban location was significant but not for suburban and wave. 

### Model check   
Is this any better than the unconditional model? 

```{r, warning=FALSE, message=FALSE}

AIC(GLMMfix0,GLMMfix1)
BIC(GLMMfix0,GLMMfix1)

## Cannot compare because different proportion of missing data.  
# test_lrt(GLMMfix0,GLMMfix1) 

```

Based on AIC and BIC the model with predictors is a better fit.  

## Predictors of growth  

If I understand correctly, I think this adds percent bipoc and percent frpl as predictors of growth. 

```{r}

GLMMfix2 <- glmer(prac_tot ~ 1 + cwave + 
                    locale + 
                    cbipoc_percent + 
                    cfrpl_percent + 
                    locale*cwave +
                    cbipoc_percent*cwave +
                    cfrpl_percent*cwave +
                    (1|school_id), 
                  family = poisson, 
                  data = main) 
summary(GLMMfix2)

## Model failed to converge. 

```

This model does not converge. 

## Test for improvement of fit

```{r}

library(performance)
test_lrt(GLMMfix1,GLMMfix2)

```

The second model does not seem to be better which would make sense given that it failed to converge.

# Plots  

```{r, warning=FALSE, message=FALSE}
library(sjPlot)
plot_model(GLMMfix1) + theme_classic () 

plot_model(GLMMfix1,type = "eff")$cwave + theme_classic () # plot the effect of Time (Wave) 

plot_model(GLMMfix1,type = "eff")$locale + theme_classic () # plot the effect of locale 
 
library(interactions) 
interact_plot(model=GLMMfix1, pred = cwave, modx = locale) # Enter the predictor of growth in the final model 
```




**No Idea if what I did above is correct**

## More Plot  

```{r, warning=FALSE, message=FALSE}
localegg <- summarySE(na.omit(main), measurevar="prac_tot", groupvars=c("locale","wave")) 

localegg$wave<-as.numeric(localegg$wave)

# The errorbars overlapped, so use position_dodge to move them horizontally
pd <- position_dodge(0.1) # move them .05 to the left and right

# Use 95% confidence interval instead of SEM

ggplot(localegg, aes(x=wave, y=prac_tot, color=locale)) + 
  geom_errorbar(aes(ymin=prac_tot-ci, ymax=prac_tot+ci), width=.1, position=pd) +
  ylab("Total Practices") +
  ylim(0,9) +
  geom_line(position=pd) +
  geom_point(position=pd) + theme_classic() + 
  scale_color_manual(values=c("cornflowerblue", "chocolate1", "darkorchid2")) +
  ggtitle("Locale x Group By Time with 95% Mean CIs") +
  theme(plot.title = element_text(hjust = 0.5, lineheight=.8, face="bold"))
  

```


# Growth model Random Effect  

Unsure if we want to include random effects for the growth model. I think it would be for wave but not sure.  

```{r}


# GLMMran1 <- glmer(prac_tot ~ 1 + wave + 
#                      locale + 
#                      bipoc_percent + 
#                      frpl_percent + 
#                      locale*wave +
#                      (1+wave|school_id), 
#                    family = poisson, 
#                    data = main) 
# summary(GLMMran1)



```
I am getting an error that the number of random effects is greater than the number of observations.  


**Attempt #2**

```{r}
library(lmerTest)
library(mice)
library(broom.mixed)
library(mitml)

md.pattern(main, rotate.names = T)


```

Tells us where the missing data is though I don't completely know how to read it. 

Okay this is from stackoverflow and is suggested as a way to manage missing data. It allows me to run the model, but I am not sure it is needed.

```{r}
#Someone online suggested this package to impute data

#### Impute ####
imp <- mice(main,
            m=5)

#### Fit With Imputations ####
fit <- with(imp,
            lmer(prac_tot ~ locale + cwave + 
                   cbipoc_percent+
                   cfrpl_percent+
                   locale*cwave+
                   cbipoc_percent*cwave+
                   cfrpl_percent*cwave+
                   (1|school_id)))

#### Pool and Summarise ####
pool <- pool(fit)
summary(pool)


#### Load Library and Get All Estimates ####
testEstimates(as.mitml.result(fit),
              extra.pars = T)
```


